```{r}
source("setup.R")
```

```{r}
data("knz_bison")
```

1. Create a new column in the bison dataset that calculates the individual’s age at the time of observation
```{r}
new_knz_bison <- knz_bison %>% 
  mutate(age = rec_year - animal_yob)
```

2. Write a function that will first filter the bison dataset based on any user-specified weight threshold (returning the filtered dataset).

```{r}
bison_weight <- function(x) {
  filtered_bison <- knz_bison %>% 
    filter(animal_weight > x) 
  
  return(filtered_bison)
  
}

bison_weight(1000)


```

3. Create a boxplot showing weight distribution between male and female bison, and then conduct a t-test to see if weight is significantly difference between males and females.

```{r}
knz_bison %>% 
  ggplot(aes(x = animal_sex, y = animal_weight)) + 
  geom_boxplot(aes(color = animal_sex))

knz_bison %>% 
  levene_test(animal_weight ~ animal_sex) # p value is very small - so we reject the null that variances are equal - variances are not equal 

knz_bison %>% 
  t_test(animal_weight ~ animal_sex, var.equal = F, detailed = T) # female bison weigh significantly more than male bison

```

